Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-08 edubots_surveys.Rnw
rev conclusions - par 6-7

The results, when grouping by experience, confirm that
experienced teachers are not afraid of changes and are willing to accept new
technological challenges; at least, in the same way that younger teachers
are. From this concrete plot it is interesting as well to observe the fact that very few
young/inexperience teachers are willing to use chatbots for other uses. This
reinforces the hypothesis thrown at the beginning of this section that younger
teachers have less experience to consider new ways of using chatbots in their daily work.

As it appears in the responses presented above, teachers’ responses are equally
distributed between positive and negative in relation to the media features:
analytics, connectivity, and hidden phone number; that is, none of them is a
prevailing factor on choosing one technology over another. However, for the features: familiarity,
horizontally, sustainability and officiality the majority provided a positive
response, designating their preference to these features. On the other hand, the
majority of teachers seems to consider not valuable the presence of official
formation, pluggability, unidirectionality and synchrony in the interaction
media features of messaging apps.

>>>>

The results, when grouping by teaching experience, confirm that
experienced teachers are just as open to change and willing to embrace new
technological challenges as younger teachers. 
From this concrete plot it is interesting as well to observe the fact that very few
young teachers are willing to use chatbots for other uses. This
reinforces the hypothesis thrown at the beginning of this section that younger
teachers have less experience to consider new ways of using chatbots in their daily work.

According to the responses presented above, teachers’ responses are evenly
split between positive and negative in relation to the media features:
analytics, connectivity, and hidden phone number. This means that none of these features is a
deciding factor in their choice of technology. However, for features such as familiarity,
horizontality, sustainability, and officiality the majority provided a positive
response, designating their preference to these features. On the other hand, the majority of teachers
do not seem to see the media features of official certification, pluggability, unidirectionality, 
and synchrony as valuable in messaging apps.
